Ceph Parallel File System Evaluation Report

### 2013-10-02 abstract.tex
cutting

Ceph is an emerging open-source parallel distributed file and storage
system. By design, Ceph is designed to leverage unreliable and commodity
storage and network hardware, and provides reliability and fault-tolerance
via controlled object placement and data replication.  Here we evaluate Ceph
for scientific high-performance computing (HPC) environments.  This paper
presents our evaluation methodology, experiments, results and observations from
mostly parallel I/O performance and scalability perspectives.  Our work makes
two unique contributions. First, our evaluation is performed under a realistic
setup for a large-scale capability HPC environment using a commercial
high-end storage system.
% (Data Direct Network's SFA10K).
%although typical in large-scale HPC environment, but atypical for average
%commercial off-the-shelf setup.  
Second, our path of investigation, tuning efforts, and findings made direct
contributions to Ceph's development and improved code quality, scalability, and
performance. These changes should benefit both Ceph and the HPC community
at large. Throughout the evaluation, we observe that Ceph is an evolving
technology under fast-paced development and shows great promises.

>>>>

Ceph is an emerging open-source parallel distributed file and storage
system. By design, Ceph is designed to leverage unreliable and commodity
storage and network hardware, and provides reliability and fault-tolerance
via controlled object placement and data replication.  
%Here we evaluate Ceph
%for scientific high-performance computing (HPC) environments.  
This paper
presents our file and block I/O performance and scalability evaluation of Ceph for
scientific high-performance computing (HPC) environments.
% methodology, experiments, results and observations from
%mostly parallel I/O performance and scalability perspectives.  
Our work makes
two unique contributions. First, our evaluation is performed under a realistic
setup for a large-scale capability HPC environment using a commercial
high-end storage system.
% (Data Direct Network's SFA10K).
%although typical in large-scale HPC environment, but atypical for average
%commercial off-the-shelf setup.  
Second, our path of investigation, tuning efforts, and findings made direct
contributions to Ceph's development and improved code quality, scalability, and
performance. These changes should benefit both Ceph and the HPC community
at large. 
%Throughout the evaluation, we observe that Ceph is an evolving
%technology under fast-paced development and shows great promises.

### 2013-10-02 introduction.tex
cutting

Oak Ridge Leadership Computing Facility (OLCF)\footnote{This research was
supported by, and used the resources of, the Oak Ridge Leadership Computing
Facility, located in the National Center for Computational Sciences at ORNL,
which is managed by UT Battelle, LLC for the U.S. DOE (under the contract No.
DE-AC05-00OR22725).} at Oak Ridge National Laboratory (ORNL) has a long history
of deploying and running very-large-scale high-performance computing (HPC)
systems\footnote{\url{http://www.top500.org/site/48553}}. 
%The facility hosted
%the Jaguar supercomputer up until recently, which was upgraded to the Titan
%supercomputer. 
In order to satisfy the I/O demand of such supercomputers, OLCF
also hosts large-scale file and storage systems. Lustre has been OLCF's choice
as the distributed parallel file system.  The latest such
large-scale file systems is Spider II\cite{spider2}.  Spider II, deployed in
2013, is designed to operate at over 1 TB/s peak aggregate I/O throughput and
has a 40 PB of raw disk capacity. As the scratch 
file system for Titan, a leadership computing platform,
Spider II emphasizes \textit{capability} over \textit{capacity}. However, we
recognize that there are a wide variety of scientific data and emerging
workloads with different performance and data access requirements (e.g., RESTful
interface, S3-like API, cloud solution integration) which might not be
efficiently serviced by Lustre. OLCF is constantly evaluating new and emerging
file and storage system technologies.

>>>>

Oak Ridge Leadership Computing Facility (OLCF)\footnote{This research was
supported by, and used the resources of, the Oak Ridge Leadership Computing
Facility, located in the National Center for Computational Sciences at ORNL,
which is managed by UT Battelle, LLC for the U.S. DOE (under the contract No.
DE-AC05-00OR22725).} at Oak Ridge National Laboratory (ORNL) has a long history
of deploying and running very-large-scale high-performance computing (HPC)
systems\footnote{\url{http://www.top500.org/site/48553}}. 
%The facility hosted
%the Jaguar supercomputer up until recently, which was upgraded to the Titan
%supercomputer. 
In order to satisfy the I/O demand of such supercomputers, OLCF
also hosts large-scale file and storage systems. Lustre has been OLCF's choice
as the distributed parallel file system.  
%The latest such
%large-scale file systems is Spider II\cite{spider2}.  Spider II, deployed in
%2013, is designed to operate at over 1 TB/s peak aggregate I/O throughput and
%has a 40 PB of raw disk capacity. As the scratch 
%file system for Titan, a leadership computing platform,
%Spider II emphasizes \textit{capability} over \textit{capacity}. 
However, we
recognize that there are a wide variety of scientific data and emerging
workloads with different performance and data access requirements (e.g., RESTful
interface, S3-like API, cloud solution integration) which might not be
efficiently serviced by Lustre. OLCF is constantly evaluating new and emerging
file and storage system technologies.
